---
title: "Managing the document data from the scopus CSV file"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
  github_document:
     number_sections: true
     toc: true
     df_print: "kable"
---


# Reading the csv file
```{r}
fileTot<-"../../Data/SCOPUS/scopus.csv"
datab <- read.csv(fileTot, h = T, row.names = NULL,sep=",")
```


# Document Ids

Column `Art..No.`:

```{r}
sum(datab$Art..No.=="")
```
Column 'DOI'

```{r}
sum(is.na(datab$DOI))
sum(datab$DOI=="")

table(datab$Document.Type,useNA = "ifany")
datab[datab$DOI=="",c("DOI","Document.Type","Title")]
datab$DOI[duplicated(datab$DOI)]
```

There are 13 papers with empty DOI, most of them are only errata and/or conference papers, but there are errata and conference papers which have their DOI. 
However there is no repetition of DOI in the table, except the 13 empty DOI.

## Creating id

It seems that the best solution would be to create an id from the first author + year + letter

```{r}
fa<-gsub(" [-A-ZÁÖÈÅŽØŁ\\.]+(,? Jr.)?I*$","",sapply(strsplit(datab$Authors, "; "),function(x)x[1]),perl = T)
# fa[order(nchar(fa),decreasing = T)]
# fa[grep(" ",fa)]
```
It appears that it is complicated to extract the last name of the first author.
Since we did the work in the code for authors, it might be smarter to use this code!

```{r}
if(file.exists("./authors.RData"))
{
  (load("./authors.RData"))
}else{
  rmarkdown::render(workOnAuthors_scopusCsv.Rmd)
  (load("./authors.RData"))
}
firstAuthors<-authDoc[authDoc$authOrder==1,c("doc","authId")]
fa<-rep(NA,nrow(datab))
fa[firstAuthors$doc]<-tabNamesFinal[firstAuthors$authId,"lastName"]
fa <- gsub("[[:punct:][:space:]]+","_",fa)
fa[is.na(fa)]<-"Anonymous"
py<-datab$Year
authYear<-paste0(fa,py)
dupliAuthYear <- duplicated(authYear)
nbRep <- table(authYear[dupliAuthYear])+1
resReplacement<-mapply(function(nb,na)list(origin=na,replacement=paste0(na,letters[1:nb])),nbRep,names(nbRep),SIMPLIFY = F)
all(sapply(resReplacement,function(a,b)length(b[b==a$origin])==length(a$replacement),b=authYear))
docId<-authYear
for(i in 1:length(resReplacement))
{
  docId[docId == resReplacement[[i]]$origin] <- resReplacement[[i]]$replacement
}
docId[grep("[a-z]$",docId)]
```

# Exporting documentsID

```{r}
save(docId,file="docId.RData")
```



# Preparing pdf download (to be done in bash with sciDownl)

```{r}
df_id_doi<-na.omit(data.frame(docId,DOI=datab$DOI))
if(!file.exists("../../vegSciLacBib_export/PDF")){dir.create("../../vegSciLacBib_export/PDF")}
file.remove("downloadPdf.sh")
writeLines(paste0("scidownl download --doi \"",df_id_doi$DOI,"\" --out ../../vegSciLacBib_export/PDF/",df_id_doi$docId,".pdf"), con="downloadPdf.sh")
```


