---
title: "Managing the author data from the scopus CSV file"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
  github_document:
     number_sections: true
     toc: true
---


# Reading the csv file
```{r}
fileTot<-"../../Data/SCOPUS/scopus.csv"
datab <- read.csv(fileTot, h = T, row.names = NULL,sep=",")
```

# Authors full names and identifiers

The colum `Author.full.names` include the full name and a scopus identifier.

```{r}
sepAuthors <- strsplit(datab$Author.full.names,"; ")
```

## Extraction with regular expression

```{r}
regexCompAuth<- "^(.+), (.+) \\(([0-9]+)\\)$"
```

It appears three authors have only a last name:

```{r}
sepAuthors[!sapply(sapply(sepAuthors,grepl,pattern=regexCompAuth),all)]
```
```{r}
regexNoFirst<- "^(.+) \\(([0-9]+)\\)$"

treatedFullNames <- lapply(sepAuthors,function(x,r1,r2)
{
  stopifnot(grepl(r1,x)|grepl(r2,x))
  regexOk <- grepl(r1,x)
  verbatim <- x
  lastName <- gsub(r1,"\\1",x)
  firstName <- gsub(r1,"\\2",x)
  authorId <- gsub(r1,"\\3",x)
  if(any(!regexOk))
  lastName[!regexOk] <- gsub(r2,"\\1",x[!regexOk])
  firstName[!regexOk] <- NA
  authorId[!regexOk] <- gsub(r2,"\\2",x[!regexOk])
  return(data.frame(
    verbatim=verbatim,
    lastName=lastName,
    firstName=firstName,
    authorId=authorId
    ))
},r1=regexCompAuth,r2=regexNoFirst)
```



# Relationships between complete author names and author names

```{r}
length(datab$Authors)==length(treatedFullNames)
sepAuthorSimp <- strsplit(datab$Authors,"; ")
all(sapply(sepAuthorSimp,length)==sapply(treatedFullNames,nrow))
tabAuthComp<-Reduce(rbind,treatedFullNames)
tabAuthComp$nameSimp<-unlist(sepAuthorSimp)
lastNameInNameSimp<-apply(tabAuthComp,1,function(x)grepl(x[2],x[5],fixed=T))
```

It appears that the order in both columns is really always the same!

# Clean extraction

Then it should be easy to extract the names in function of the author ID

```{r}
require(sqldf)
extractMajoNames<-by(tabAuthComp,tabAuthComp$authorId,function(tab)
  {
    lnfnOrder<-sqldf("SELECT lastName, firstName, count(*) FROM tab ORDER BY count(*) DESC,LENGTH(firstName) DESC LIMIT 1")
    nbns<-table(tab$nameSimp)
    nsMaj<-names(nbns)[which.max(nbns)]
    data.frame(lastName=lnfnOrder$lastName,firstName=lnfnOrder$firstName,nameSimp=nsMaj)
    
  })
tabNamesFinal<-Reduce(rbind,extractMajoNames)
rownames(tabNamesFinal)<-names(extractMajoNames)
authIdsDoc<-sapply(treatedFullNames,function(x)x$authorId)
authDoc<-data.frame(
  doc=rep(1:length(authIdsDoc),sapply(authIdsDoc,length)),
  authId=unlist(authIdsDoc),
  authOrder=unlist(lapply(authIdsDoc[sapply(authIdsDoc,length)>0],function(x)1:length(x))),
  authNb=rep(sapply(authIdsDoc,length),sapply(authIdsDoc,length)),
  authSimp=tabAuthComp$nameSimp
)
```



# tests

```{r}
sepAbbAuthors <- strsplit(datab$Authors,"; ")
regexAbbAuthors <- "^.+ ((-?[A-Z]?[a-z]?\\.)+)$"
regexAbbAuthors <- "^.+ ([.[:alpha:]-]+)$"

sepAbbAuthors[sapply(sapply(sapply(sepAbbAuthors,grepl,pattern=regexAbbAuthors,perl=T),`!`),any)]



all(sapply(sepAbbAuthors,length) == sapply(sepAuthors,length))

allInOne<-Reduce(rbind,treatedFullNames)
length(unique(allInOne$authorId))
A<-tapply(allInOne$verbatim,allInOne$authorId,unique)
A[sapply(A,length)>1]
B<-tapply(allInOne$lastName,allInOne$authorId,unique)
B[sapply(B,length)>1]
```

