---
title: "Managing the affiliation data from the scopus CSV file"
author: "Marius Bottin"
date: "`r Sys.Date()`"
output: 
  github_document:
     number_sections: true
     toc: true
---


# Reading the csv file
```{r}
fileTot<-"../../Data/SCOPUS/scopus.csv"
datab <- read.csv(fileTot, h = T, row.names = NULL,sep=",")
```

# The affiliation column

The column `Authors.with.affiliations` allows to link authors and institutions


```{r}
head(datab$Authors.with.affiliations)
sepAffil <- lapply(strsplit(datab$Authors.with.affiliations,"; "),strsplit,", ")
```


```{r}
head(datab$Authors)
sepAuthorSimp<-strsplit(datab$Authors,"; ")
#mapply(function(x,y)x==sapply(y,function(z)z[[1]]),sepAuthorSimp,sepAffil)
```
# Going further

Some authors are not present in the affiliations?

```{r}
A<-which(!sapply(mapply(function(x,y)x%in%unlist(y),sepAuthorSimp,sepAffil),all))
res<-mapply(list,sepAuthorSimp[A],sepAffil[A],SIMPLIFY = F)
```
The problems seems to come from the facts that 

1. some of the authors have comma in their name string... (e.g. "Cahill J.F., Jr.")
1. some of the papers simply do not have any affiliation:

```{r}
which(datab$Authors.with.affiliations=="")
```

This means we should not use the separation by ";" for the affiliations but instead look for the author names, separate 

## Another way to extract affiliation by authors


First we extract the adress (character number) of the match of the author name in the affiliation string.

```{r}
#mapply(function(str,seps)strsplit(x=str,split=seps),datab$Authors.with.affiliations,sepAuthorSimp)[1:10]
#sapply(mapply(function(str,seps)lapply(seps,gregexpr,text=str,fixed=T),datab$Authors.with.affiliations,sepAuthorSimp),length)==sapply(sepAuthorSimp,length)
charBegAuth <- mapply(function(str,seps)lapply(seps,gregexpr,text=str,fixed=T),datab$Authors.with.affiliations,sepAuthorSimp)
```

Sometimes 2 authors of the same paper have the same simplified name

```{r}
refRepAuth<-sapply(sepAuthorSimp,function(x){
  ref<-integer(length(x))
  ref[1]<-1
  if(length(x)>1){
    for(i in 2:length(x))
    {ref[i]<-1+sum(x[1:(i-1)]==x[i])}
  }
  return(ref)
  })
charBegAuth<-mapply(function(docx,docy){mapply(function(authx,authy)authx[[1]][authy],docx,docy)},charBegAuth,refRepAuth)
names(charBegAuth)<-NULL
stopifnot(all(sapply(charBegAuth,length)==sapply(sepAuthorSimp,length)))
stopifnot(all(unlist(sapply(charBegAuth,function(x){if(length(x)==0){return(T)}else{return(order(x)==1:length(x))}}))))
```

```{r}
resAffil<-list()
for(doc in 1:length(sepAuthorSimp))
{
  resAffil[[doc]]<-character(length(sepAuthorSimp[[doc]]))
  if(length(sepAuthorSimp[[doc]])==0){next}
  names(resAffil[[doc]])<-sepAuthorSimp[[doc]]
  for(auth in 1:length(sepAuthorSimp[[doc]])){
    if(charBegAuth[[doc]][auth]==-1){
      resAffil[[doc]][auth]<-""
    }else{
      firstAuth<-auth==1
      lastAuth<-auth==length(sepAuthorSimp[[doc]])
      end<-ifelse(lastAuth,nchar(datab$Authors.with.affiliations[doc]),charBegAuth[[doc]][[auth+1]]-1)
      beg<-charBegAuth[[doc]][[auth]]+nchar(sepAuthorSimp[[doc]][auth])
      resAffil[[doc]][auth]<-substr(datab$Authors.with.affiliations[doc],beg,end)
    }
  }
}
resAffil<-lapply(resAffil,function(x)gsub("[[:punct:][:space:]]*$","",gsub("^[[:punct:][:space:]]*","",x)))
sepAffil<-lapply(resAffil,strsplit,", ")
```




There are various problems with the separating fields operation here:

* when there are comma in an expression (e.g faculty of plant, animal and ecology)...
* when there are opening parenthesis and "," or ";" before ending the parentheses

# Parenthesis problem

Concerning the parentheses:

Let's try and find the closing parentheses which are not associated with opening parenthesis:

```{r}
pbI<-integer()
pbJ<-integer()
pbK<-integer()
for(i in 1:length(sepAffil))
{
  if(length(sepAffil[[i]])==0){next}
  for(j in 1:length(sepAffil[[i]]))
  {
    A<-grep("^[^(]+\\)",sepAffil[[i]][[j]])
    pbI<-c(pbI,rep(i,length(A)))
    pbJ<-c(pbJ,rep(j,length(A)))
    pbK<-c(pbK,A)
  }
}
```

Showing the problems

```{r}
for(i in 1:length(pbI))
{
  print(sepAffil[[pbI[i]]][[pbJ[i]]])
}
```


Finding the potential resolutions:

```{r}
resolK<-integer(length(pbI))
resolJK<-integer(length(pbI))
for(i in 1:length(pbI))
{
  A<-grep("\\([^)]+$",sepAffil[[pbI[i]]][[pbJ[i]]][1:pbK[[i]]])
  if(length(A)!=0){
    resolK[i]<-A[length(A)]
    resolJK[i]<-pbJ[i]
  }else{
    if(pbJ[i]>1){
      A<-grep("\\([^)]+$",sepAffil[[pbI[i]]][[pbJ[i]-1]])
      if(length(A)!=0){
        resolK[i]<-A[length(A)]
        resolJK[i]<-pbJ[i]-1
      }else{
        resolK[i]<-NA
        resolJK[i]<-NA
      }
    }else{
      resolK[i]<-NA
      resolJK[i]<-NA
    }
  }
}
```

Showing the resolution
```{r}
for(i in 1:length(pbI))
{
  cat("problem",i,":",pbI[i],ifelse(is.na(resolJK[i])|resolJK[i]==pbJ[i],pbJ[i],paste(resolJK[i],pbJ[i],sep="-")),pbK[i],"resol:",resolK[i],"\n")
  print(sepAffil[[pbI[i]]][unique(c(resolJK[i],pbJ[i]))])
  cat("Resolution:\n")
  if(!is.na(resolK[i])&pbJ[i]==resolJK[i])
  {
    print(paste(sepAffil[[pbI[i]]][[pbJ[i]]][resolK[i]:pbK[i]],collapse=", "))
    cat("\n\n")
  }else{
    if(!is.na(resolK[i])&pbJ[i]!=resolJK[i])
    {
      print(paste(c(sepAffil[[pbI[i]]][[resolJK[i]]][resolK[i]:length(sepAffil[[pbI[i]]][[resolJK[i]]])],
                    sepAffil[[pbI[i]]][[pbJ[i]]][1:pbK[i]])
                    ,collapse=", "))
      cat("\n\n")
    }else{
      cat("!!!!! No solution !!!!!!!!!!\n\n")}
  }
}
```

Applying resolution:

```r
for(i in 1:length(pbI))
{
  if(is.na(resolJK[i])){next}
  # same J (author)
  if(pbJ[i]==resolJK[i]){
  ## prepare the resolution (sep by ",")
    sepAffil[[pbI[i]]][[pbJ[i]]][resolK[i]] <- paste(sepAffil[[pbI[i]]][[pbJ[i]]][resolK[i]:pbK[i]], collapse = ", ")
  ## suppress the affected K
    toSuppress<-(resolK[i]+1):pbK[i]
    sepAffil[[pbI[i]]][[pbJ[i]]]<-sepAffil[[pbI[i]]][[pbJ[i]]][-toSuppress]
  ## if any other problems in the same J, later K change numbers of problems and resolutions
    w_same<-which(pbI==pbI[i]&pbJ==pbJ[i])
    w_same<-w_same[w_same>i]
    if(length(w_same)>0)
    {
      pbK[w_same]<-pbK[w_same]-length(toSuppress)
      resolK[w_same]<-resolK[w_same]-length(toSuppress)
    }
  }
  
  # (wrongly) different J 
  ## prepare the resolution (J sep by ";", K sep by ","), followed by wrongly affected different j
  ## suppress the affected k and j
  ## if any other problem in the same I, change J and K numbers

}
```
The difficulty is that the numbers of elements from the list depends on the corrections we make... Then maybe doing everything in a ´while´ loop (to be able to control better the counters) might result better

```{r}
keep<-sepAffil
checkItOut<-data.frame(i=integer(0),j=integer(0),k=integer(0))
i<-1
while(i<=length(sepAffil))
{
  #cat("i",i,"\n")
  if(length(sepAffil[[i]])==0){i<-i+1}
  j<-1
  while(j<=length(sepAffil[[i]]))
  {
    #cat("j",j,"\n")
    k<-1
    while(k<=length(sepAffil[[i]][[j]]))
    {
      #cat("k",k,"\n")
      if(any(grepl("\\([^)]+$",sepAffil[[i]][[j]][k:length(sepAffil[[i]][[j]])])))
      {
        w<-grep("\\([^)]+$",sepAffil[[i]][[j]])
        k<-w[w>=k]
        cat("i",i,"j",j,"k",k,"...")
        checkItOut<-rbind(checkItOut,data.frame(i=i,j=j,k=k))
        # Do everything here
        closingParenthesis <- grep("^[^(]+\\)",sepAffil[[i]][[j]])
        if(length(closingParenthesis)>0){
          cl<-closingParenthesis[1]
          sepAffil[[i]][[j]][k]<-paste(sepAffil[[i]][[j]][k:cl],collapse=", ", sep=", ")
          toSupp <- (k+1):cl
          sepAffil[[i]][[j]]<-sepAffil[[i]][[j]][-toSupp]
          cat("done\n")
        }else{
          j2<-j+1
          closingParenthesis <- grep("^[^(]+\\)",sepAffil[[i]][[j2]])
          if(length(closingParenthesis)>0){
            cl<-closingParenthesis[1]
            sepAffil[[i]][[j]][k]<-
              paste(
                paste(sepAffil[[i]][[j]][k:length(sepAffil[[i]][[j]])],collapse=", ", sep=", "),
                paste(sepAffil[[i]][[j2]][1:cl],collapse=", ", sep=", ")
                ,sep="; ")
            if(length(sepAffil[[i]][[j]])>k){
              toSupp <- (k+1):length(sepAffil[[i]][[j]])
              sepAffil[[i]][[j]]<-sepAffil[[i]][[j]][-toSupp]
            }
            sepAffil[[i]][[j]]<-c(sepAffil[[i]][[j]],sepAffil[[i]][[j2]][(cl+1):length(sepAffil[[i]][[j2]])])
            sepAffil[[i]]<-sepAffil[[i]][-j2]
            cat("done next\n")
          }else{
            cat("unresolved\n")
          }
        }
        k<-k+1
      }else{k<-length(sepAffil[[i]][[j]])+1}
    }
      
    j<-j+1
  }
  i<-i+1
  #cat("n\n")
}
```


```{r}
ln_affil <- sapply(sepAffil,sapply,length)
tabAffil<-data.frame(
  doc=rep(1:length(sepAffil),sapply(ln_affil,function(x)ifelse(length(x)==0,0,sum(x)))),
  auth=unlist(lapply(sepAffil[sapply(sepAffil,length)>0],function(x)rep(1:length(x),sapply(x,length)))),
  string=unlist(sepAffil)
)
```

# countries

One easy thing to do which could help us make sense of the data here would be to recognize all country fields. Then we could maybe have an idea of the number of affiliations by authors...
That would mean downloading a dataset that contains all country names, in various languages in case!


```{r}
require(rnaturalearth)
require(rnaturalearthdata)
require(sf)
worldMap_tot<-ne_countries(returnclass = "sf")
tinyCountries<-ne_download(type="admin_0_tiny_countries",returnclass = "sf")

colnames(worldMap_tot)[grepl("name",colnames(worldMap_tot))]
head(worldMap_tot)
colnames(tinyCountries)
names_toKeep<-c("formal_en","name","name_long","name_en","name_es","name_pt","name_fr")
toupper(names_toKeep) %in% colnames(tinyCountries)
countryNames<-Reduce(rbind,lapply(names_toKeep,function(x,t1,t2,t3){
  tab1<-data.frame(string=st_drop_geometry(t1[,x]),name=st_drop_geometry(t1["name"]),type=x)
  tab2<-data.frame(string=st_drop_geometry(t2[,toupper(x)]),name=st_drop_geometry(t2["NAME"]),type=x)
  if(x%in%colnames(t3)){
    tab3<-data.frame(string=st_drop_geometry(t3[,x]),name=st_drop_geometry(t3["name"]),type=x)
  }else{
    tab3<-data.frame(string=character(0),name=character(0),type=character(0))
  }
  colnames(tab1)<-colnames(tab2)<-colnames(tab3)<-c("string","name","type")
  return(rbind(tab1,tab2,tab3))},t1=worldMap_tot,t2=tinyCountries,t3=map_units50))
countryNames[!duplicated(countryNames$string),]
countryNames<-rbind(countryNames,
                    data.frame(
                      string=c("Democratic Republic Congo","Cote d'Ivoire"),
                      name=c("Dem. Rep. Congo","Côte d'Ivoire"),
                      type="manual"
                    ))
list_countryAffil<-list()
for(i in 1:length(sepAffil)){
  list_countryAffil[[i]]<-list()
  if(length(sepAffil[[i]])==0)next
  for(j in 1:length(sepAffil[[i]]))
  {
    list_countryAffil[[i]][[j]]<-sepAffil[[i]][[j]]%in%countryNames$string
  }
}
nbCountriesByAuthors<-lapply(list_countryAffil,sapply,sum)
noCountry<-sapply(nbCountriesByAuthors,function(x)which(x==0))
nb_noCountry<-sapply(noCountry,function(x)length(x))
tabNoCountryRef<-data.frame(
  doc=rep(which(nb_noCountry!=0),nb_noCountry[nb_noCountry>0]),
  auth=unlist(noCountry)
)
apply(tabNoCountryRef,1,function(x,l)l[[x[1]]][[x[2]]],l=sepAffil)
```
# States

```{r}
A<-lapply(list_countryAffil,lapply,function(x)which(x)-1)
potentialStates<-character(0)
#for(i in 1:length(A))
#  for(j in 1:length(A[[i]]))
#    potentialStates<-c(potentialStates,sepAffil[[i]][[j]][A[[i]][[j]]])
```



```{r}
states<-ne_states(returnclass="sf")
states$name
which(!states$adm0_a3%in%worldMap_tot$adm0_a3)
states[!states$geonunit %in% countryNames$string,]$name
st_drop_geometry(states[states$geonunit %in% countryNames$string,c("name","geonunit","admin","type_en","name_local","postal")])
```


# Cities

```{r}
require(geojsonR)
cityData <- FROM_GeoJson("../../Data/geog/geonames-all-cities-with-a-population-1000.geojson")
namesCity1<-data.frame(string=sapply(cityData$features,function(x)x$properties$name),
                       name=sapply(cityData$features,function(x)x$properties$name),
                       country=sapply(cityData$features,function(x) ifelse(length(x$properties$cou_name_en)==0,NA,x$properties$cou_name_en)),
                       population=sapply(cityData$features,function(x)x$properties$population)
)
alternateNames<-lapply(cityData$features,function(x)unlist(x$properties$alternate_names))
alterNameCity<-data.frame(string=unlist(alternateNames),
           name=rep(namesCity1$string,sapply(alternateNames,length)),
           country=rep(namesCity1$country,sapply(alternateNames,length)),
           population=rep(namesCity1$population,sapply(alternateNames,length))
)
cityTab<-rbind(namesCity1,alterNameCity)
cityTab<-cityTab[order(cityTab$population,decreasing = T),]
```

```r
list_cityAffil<-list()
for(i in 1:length(sepAffil)){
  list_cityAffil[[i]]<-list()
  if(length(sepAffil[[i]])==0)next
  for(j in 1:length(sepAffil[[i]]))
  {
    list_cityAffil[[i]][[j]]<-sepAffil[[i]][[j]]%in%cityTab$string
  }
}
```
# Analysis countries and cities

```{r}
tabAffil$country<-tabAffil$string%in%countryNames$string
tabAffil$city<-tabAffil$string%in%cityTab$string
doc_auth<-paste(tabAffil$doc,tabAffil$auth,sep="_")
hasCountry<-tapply(tabAffil$country,doc_auth,any)
hasCity<-tapply(tabAffil$city,doc_auth,any)
```


Number of affiliations having country and city:

```{r}
table(hasCountry,hasCity)
```

10 examples of not having country:

```{r}
A<-sample(names(hasCountry)[!hasCountry],10)
tapply(tabAffil$string[doc_auth%in%A],doc_auth[doc_auth%in%A],paste,collapse=", ")
```


10 examples of not having city:

```{r}
A<-sample(names(hasCity)[!hasCity],10)
tapply(tabAffil$string[doc_auth%in%A],doc_auth[doc_auth%in%A],paste,collapse=", ")
```


Note: problems to resolve to get better results:

1. Sometimes we get the city with a postal code (sometimes with the country code)
1. sometimes we get an address
1. sometimes we get Cedex


## counting the affiliations based on cities and countries

```{r}
nbCountry<-tapply(tabAffil$country,doc_auth,sum)
nbCity<-tapply(tabAffil$city,doc_auth,sum)

table(nbCountry==nbCity)
table(nbCountry)
table(nbCity)
more3Countries<-names(nbCountry[nbCountry>3])
# tapply(tabAffil$string[doc_auth%in%more3Countries],doc_auth[doc_auth%in%more3Countries],paste,collapse=", ")

```



```{r}
listUniv<-tabAffil$string[grepl("\\<univ", tabAffil$string,ignore.case = T)]
```


```{r}
write.csv(tabAffil,file="../../vegSciLacBib_export/tabAffil.csv")
```